Multisymplectic observables and higher Courant algebroids

### 2024-02-27 msgauge-Caprarola.tex
Caprarola - Finished slides

%%-------------------------------------------------------------------------------------------------------------------------------------------------
%\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
%	Given a \alert{symplectic mfd.} $(M,\omega)$ ...
%	\vfill
%	\begin{center}
%		\includestandalone[width=.95\textwidth]{Pictures/Frame_Embedding_Diagram_symplectic}
%	\end{center}
%	\vspace{3em}
%	\vfill
%	\begin{minipage}[t][8.5em][t]{\textwidth}
%		\begin{itemize}
%			\item<1-> \alert<1>{... there is a naturally associated Poisson algebra ...}
%			\item<2-> \alert<2>{... and also a (standard twisted) Lie Algebroid}.
%			\item<3-> A Lie algebroid is a "controlled" \alert<3>{$\infty$-dimensional Lie algebra.}
%			\item[]<4->
%				\quad\\
%		\vspace{-.75em}
%		\tcbset{colback=white,
%		colbacktitle=white,
%		colframe=red!70!black,
%		boxrule=1pt,
%		colupper=red!70!black,
%		arc=15pt,
%		}
%		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
%			\color{blue}{
%			\textbf{Lemma}: There exists an embedding of Lie Algebras.
%			}
%		\end{tcolorbox}
%		\end{itemize}
%	\end{minipage}
%\end{frame}
%%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

%%-------------------------------------------------------------------------------------------------------------------------------------------------
%\begin{frame}[fragile]{Compatibility between gauge transformations and comoment maps}
%	%
%	Consider $(M,\omega)$ \alert{symplectic mfd.}
%	%
%	\begin{center}
%			\includestandalone[width=.8\textwidth]{Pictures/Frame_BigDiagram_symplectic}
%	\end{center}
%	%
%	\vspace{-1em}
%	\vfill
%	\begin{minipage}[t][8em][t]{\textwidth}
%		\begin{itemize}
%			\only<2>{
%				\item<2-> Consider a second gauge-related symplectic structure on $M$
%					\begin{displaymath}
%						\tilde{\omega} = \omega + d B \qquad \text{with} \quad B\in \Omega^1(M).
%					\end{displaymath}
%			}
%			\only<3-4>{
%				\item<3-> There is a natural isomorphism in the Lie Alg.oids category \emph{($B$-transformation)}
%					\begin{displaymath}
%						\binom{x}{f} \mapsto \binom{x}{f-\iota_x B} ~.
%					\end{displaymath}
%			}
%			\only<6-7>{
%				\item<6-> Consider an infinitesimal group action $\mathfrak{g}\circlearrowleft M$ which is Hamiltonian w.r.t. both $\omega$ and $\tilde{\omega}$.
%				\item<7-> let be $f:\mathfrak{g} \to C^\infty(M)_\omega$ and $\tilde{f}:\mathfrak{g} \to C^\infty(M)_{\tilde{\omega}}$ two comoment map s.t.
%				\begin{displaymath}
%					\tilde{f}(\xi) = f(\xi) - \iota_{\underline{\xi}}B
%				\end{displaymath}
%				}
%			\item[]						
%		\end{itemize}
%	\only<5>{
%		\vspace{-.75em}
%		\begin{center}
%		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
%			\alert{
%			\faQuestionCircle \qquad
%				{How can we close the left-hand side?}
%			\qquad \faQuestionCircle		
%			}
%		}
%		\end{center}
%	}
%	\only<8->{
%		\vspace{-.75em}
%		\tcbset{colback=white,
%		colbacktitle=white,
%		colframe=red!70!black,
%		boxrule=1pt,
%		colupper=red!70!black,
%		arc=15pt,
%		}
%		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
%			\color{blue}{
%			Lemma: The central pentagon commutes!
%			}
%		\end{tcolorbox}
%	\vfill
%	}
%	\only<9->{
%		\vspace{-.75em}
%		\begin{center}
%		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
%			\alert{
%			\faQuestionCircle \qquad
%				{What happens in the higher (n-plectic) case?}
%			\qquad \faQuestionCircle		
%			}
%		}
%		\end{center}
%	}
%	\end{minipage}	
%\end{frame}
%\note[itemize]{
%	\item The horizontal embedding is  $f \mapsto (v_f,f)$;
%	\item Vertical maps are also known as \emph{Gauge transformations}
%	\item upshot: 
%	\begin{enumerate}
%		\item 
%	\end{enumerate}
%}
%%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

%##################################################################################
\begin{frame}
	\begin{center}
	\Huge\emph{Outlook}
	\end{center}
\end{frame}
\addtocounter{framenumber}{-1}
%##################################################################################

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A bigger picture about Multisymplectic observables}
	OUTLOOK. La big picture. 
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

%---------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Leibniz-algebra of Observables}
\begin{frame}[fragile,t]{Leibniz-algebra of Observables}

@@

>>>>

@@

@@

%##################################################################################
\section*{Outlook}
\begin{frame}
	\begin{center}
	\Huge\emph{Outlook}
	\end{center}
\end{frame}
\addtocounter{framenumber}{-1}
%##################################################################################

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A bigger picture about Multisymplectic observables}
	%
	\begin{center}
		\includestandalone[width=.95\textwidth]{Pictures/Frame_OutlookDiagram}
	\end{center}

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Pentagonal Diagram and higher Prequantization}
	%
	\begin{center}
		\includestandalone[width=.8\textwidth]{Pictures/Frame_OutlookPrequantum}
	\end{center}		
	\onslide<3->{
		\small
		\begin{block}{Partial Results in the $2$-plectic case}
			\begin{itemize}
				\item G. Sevestre \& T. Wurzbacher, "On the Prequantisation Map for 2-Plectic Manifolds",  \cite{Sevestre2021};
				\item D. Djounvouna \& D. Krepski, "Infinitesimal symmetries of bundle gerbes and Courant algebroids"\cite{Djounvouna2023}.
			\end{itemize}
		\end{block}
	}
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

@@

%---------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile,t]{Leibniz-algebra of Observables}
